---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# multiEnrichment

<!-- badges: start -->
<!-- badges: end -->

The multiEnrichment package offers four multi-omics enrichment analysis algorithms: mitch, multiGSEA, ActivePathways, and multiNetEnrich, and it supports multi-omics analysis using clusterProfiler. multiEnrichment standardizes input and output formats, and its results can be visualized using enrichplot.


## :writing_hand: Authors
Erqiang Hu

 Department of Bioinformatics, School of Basic Medical Sciences, Southern Medical University.


## :arrow\_double\_down: Installation


You can install the released version of multiEnrichment from [Github](https://github.com/huerqiang/multiEnrichment/tree/master) with:

``` r
devtools::install_github("huerqiang/multiEnrichment")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r message=FALSE, warning=FALSE}
library(multiEnrichment)
## basic example code
```
